So you've decided to detonate helium

### 2020-08-07 simplified_sdc_intro/paper.tex
move this into an intro paper the detonation part will live on in a separate paper

\documentclass[times,modern]{aastex62}

@@

\subsection{Reaction Convergence}

\subsection{Flames}

ECSNe flames

aprox13 flames

simplified-SDC takes 3x more timesteps than Strang

look at number of right hand side calls

\subsection{Detonations}

Our focus here is modeling helium detonations.  Previously, we
showed~\cite{katzzingale:2019} that accurate modeling the ignition of
a detonations requires a resolution such that $\tau_s < \tau_e$, where
$\tau_s = \Delta x/c_s$ is the sound crossing time of a zone and
$\tau_e = e/\dot{e}$ is the nuclear energy injection timescale.  For
the detonations explored here, we will work in that regime.

Helium detonations can be important in different models of Type Ia
supernova.  In the double detonation model for Type Ia supernovae, a
helium detonation is used to trigger a carbon detonation in the
underlying white dwarf.  White dwarf collisions or mergers can have
helium detonations if there is a thin layer of helium on the surface
of the white dwarfs.  We will model two densities, $2\times
10^6~\gcc$, e.g., as used in \citet{glasner:2018} for double
detonation models, and $10^7~\gcc$ to see the effects at higher
densities.

Effect of number of SDC iterations

Effect of timestep

Effect of resolution

Difference densities?

\begin{figure}[t]
\centering
\plotone{strang_timestep}
\caption{\label{strang_timestep} Effect of timestep size on the detonation using Strang splitting.}
\end{figure}

\begin{figure}[t]
\centering
\plotone{sdc_iters}
\caption{\label{sdc_iters} Effect of number of SDC iterations detonation.}
\end{figure}

\begin{figure}[t]
\centering
\plotone{sdc_timestep}
\caption{\label{sdc_timestep} Effect of timestep size on the detonation using the SDC method.}
\end{figure}

\begin{figure}[t]
\centering
\plotone{strang_sdc_compare}
\caption{\label{strang_vs_sdc} Comparison of Strang and SDC on the detonation problem.}
\end{figure}

Something about expense?  We can just compare CPU time.

\subsection{Massive Star}

we need to look at the number of RHS calls spatially

also need to look at tolerances in the burner

analytic Jacobian run is much faster

what does Strang run do

\subsection{X-ray bursts}

crashed with too many subcycles.  Need to rerun with new Jacobian

\subsection{Hydro and Gravity}

Merging stars

it doesn't run more than a few steps with simplified SDC

has a small density error and too many subcycles after ~ 128 steps

>>>>

\documentclass[times,modern]{aastex63}

@@
